---
title: "Report"
output:
  pdf_document: 
    toc: true
  word_document: 
    toc: true
  html_document: 
    toc: true
params: 
  choice_data: NA
  time_choice_token: NA
  token_choosen_sentence: NA
  token_choosen_word: NA
  token_choosen_norma: NA
  overview_choice_data_all: NA
  overview_choice_data_num_check: NA
  overview_choice_offset: NA
  overview_choice_num_word: NA
  overview_choice_book: NA
  data_complete: NA
  data_selected_plot: NA
  min_freq_wordcloud: NA
  max_freq_wordcloud: NA
  max_word_wordcloud: NA
  key: NA
  selected_word_cloud: NA
always_allow_html: yes
---

```{r setup, cache = TRUE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
d <- params$data_complete
ds <- params$data_selected_plot
mifw <- params$min_freq_wordcloud
mafw <- params$max_freq_wordcloud
mww <- params$max_word_wordcloud
l <- length(ds$rowname)
key <- params$key
```

#Parameters

Data number: `r params$choice_data`

Choice of tokenization:   

* `r params$time_choice_token`
* sentence `r params$token_choosen_sentence`
* word `r params$token_choosen_word`
* normalization `r params$token_choosen_norma`
                          
Choice of data in the pre-processing overview: 

* all `r params$overview_choice_data_all`
* numeric input `r params$overview_choice_data_num_check`
    + number word `r params$overview_choice_num_word`
    + offset `r params$overview_choice_offset`
* book `r params$overview_choice_book`

The parameters chosen in this analysis are the frequencies between `r mifw` and `r mafw`, and a maximum number of words of `r mww` for the wordcloud.
Selected word in the wordcloud: `r if(is.null(params$selected_word_cloud)){"None"} else{params$selected_word_cloud} `

#Overview 

You can see just below the different plots of the overview: 

```{r}
p1 <- plot_ly(d, x = ~rowname, y = ~freq, key = ~key, type = 'scatter', mode='lines+markers',  marker = list(color = 'blue', opacity=2))%>%layout(title = 'Frequency according to the word', xaxis = list(title ='Word'), yaxis =list(title ='Frequency'), titlefont = 'arial', showlegend = FALSE)
tmpFile <- tempfile(fileext = ".png")
export(p1, file = tmpFile)

p2 <- plot_ly(d, x = ~rowname, y = ~tf, key = ~key, type = 'scatter', mode='lines+markers',  marker = list(color = 'blue', opacity=2))%>%layout(title = 'Term Frequency according to the word', xaxis = list(title ='Word'), yaxis =list(title ='Term Frequency'), titlefont = 'arial', showlegend = FALSE)
tmpFile <- tempfile(fileext = ".png")
export(p2, file = tmpFile)
```

#Filter

##Plots

You can see here the different plots of the overview after selection of the interesting points:

```{r}
if(l!=0){
  key_part = row.names(ds)
  
  p3 <- plot_ly(ds, x = ~rowname, y = ~freq, key = ~key_part, type = 'scatter', mode='lines+markers',  marker = list(color = 'blue', opacity=2))%>%layout(title = 'Frequencies according to the selected words', xaxis = list(title ='Word'), yaxis =list(title ='Frequency'), titlefont = 'arial', showlegend = FALSE)
  tmpFile <- tempfile(fileext = ".png")
  export(p3, file = tmpFile)
}
```

```{R}
if(l!=0){
  p4 <- plot_ly(ds, x = ~rowname, y = ~tf, key = ~key_part, type = 'scatter', mode='lines+markers',  marker = list(color = 'blue', opacity=2))%>%layout(title = 'Term Frequencies according to the selected words', xaxis = list(title ='Word'), yaxis =list(title ='Term Frequency'), titlefont = 'arial', showlegend = FALSE)
  tmpFile2 <- tempfile(fileext = ".png")
  export(p4, file = tmpFile2)
}
```

##Table

Here is the table with the selected points from the overview:

```{r}
if(l){
kable(ds, caption ="Table of the data selected in the plot")
}
```

##Wordcloud

You can see just below the wordcloud with the interesting points :

```{r}
bp.cols<- c("light blue","cornflowerblue", "coral2", brewer.pal(8,"Dark2"))
dsw <- data.frame(ds$word, ds$freq)
dswf <- head(subset(dsw, dsw$ds.freq <= mafw & dsw$ds.freq >= mifw), mww)
if(l){
  library(wordcloud)
  #This part is to add a title to the wordcloud. In order to do that, you have to change the layout before adding the title. It is explained here :     https://stackoverflow.com/questions/15224913/r-add-title-to-wordcloud-graphics-png
  layout(matrix(c(1, 2), nrow=2), heights=c(1, 4))
  par(mar=rep(0, 4))
  plot.new()
  text(x=0.5, y=0.5, cex = 0.8, "Wordcloud 1 : Wordcloud of the selected points")
  #This is where we do the wordcloud, adding some colors and some other features.
  wordcloud(dswf$ds.word, dswf$ds.freq, random.order=FALSE,rot.per=0.40,use.r.layout=FALSE, random.color=TRUE,colors=bp.cols, main=text)
}
#w <- wordcloud2(data = dswf, shape = 'star', size = 0.8, shuffle =FALSE)
#tmpFile <- tempfile(fileext = ".png")
#export(w, file = tmpFile)
```