---
title: "Report"
output:
  pdf_document: 
    toc: true
    toc_depth: 4
  word_document: 
    toc: true
    toc_depth: 4
  html_document: 
    toc: true
    toc_depth: 4
params: 
  choice_data: NA
  time_choice_token: NA
  token_choosen_sentence: NA
  token_choosen_word: NA
  token_choosen_norma: NA
  overview_choice_data_all: NA
  overview_choice_data_num_check: NA
  overview_choice_offset: NA
  overview_choice_num_word: NA
  overview_choice_book: NA
  data_selected_lines: NA
  data_boxplot: NA
  data_complete: NA
  boxplot_1_data: NA
  boxplot_2_data: NA
  boxplot_3_data: NA
  boxplot_4_data: NA
  boxplot_5_data: NA
  result_choice_box_1: NA
  result_choice_box_2: NA
  result_choice_box_3: NA
  result_choice_box_4: NA
  result_choice_box_5: NA
  occurence_word: NA
  occurence_stop_word: NA
  regression_lin: NA
  result_zipfs_law_passed: NA
  table_info_laws: NA
  stop_words: NA
  stemming: NA
  data_selected_plot: NA
  data_table_selected_plot: NA
  min_freq_wordcloud: NA
  max_freq_wordcloud: NA
  max_word_wordcloud: NA
  key: NA
  selected_word_cloud: NA
  sentences_selected_cloud: NA
  data_last_wordcloud: NA
always_allow_html: yes
---

```{r setup, cache = TRUE, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
data_lines <- params$data_selected_lines
d_token_boxplot <- params$data_boxplot
K <- exp(params$regression_lin$coefficients[[1]])
beta <- params$regression_lin$coefficients[[2]]
zipfs_law_result <- params$result_zipfs_law_passed
d <- params$data_complete
ds <- params$data_selected_plot
mifw <- params$min_freq_wordcloud
mafw <- params$max_freq_wordcloud
mww <- params$max_word_wordcloud
l <- length(ds$rowname)
key <- params$key
d_last_wd <- params$data_last_wordcloud
```

#Parameters

```{r}
if(length(params$overview_choice_book)==0){
  books_selected <- "No book selected"
} else{
  books_selected <- params$overview_choice_book
}
if(length(params$selected_word_cloud)==0){
  selected_cloud_word <- "No word selected in the wordcloud"
} else{
    selected_cloud_word <- params$selected_word_cloud
} 

if(params$overview_choice_data_all==FALSE & params$overview_choice_data_num_check == FALSE & length(params$overview_choice_book)==0){
  result_selection <- paste("From line ", data_lines$rowname[1], "to line ", data_lines$rowname[length(data_lines$rowname)])
} else{
  result_selection <- "No data has been selected by hand"

}

if(NROW(ds)==0){
  result_selection_analysis <- "No data has been selected"
} else{
  result_selection_analysis <- paste("From line ", ds$rowname[1], "to line ", ds$rowname[length(ds$rowname)])
}
```

Data number: `r params$choice_data`

Choice of tokenization:   

* `r params$time_choice_token`
* sentence `r params$token_choosen_sentence`
* word `r params$token_choosen_word`
* normalization `r params$token_choosen_norma`
                          
Choice of data in the pre-processing overview: 

* all: `r params$overview_choice_data_all`
* numeric input: `r params$overview_choice_data_num_check`
    + number word `r params$overview_choice_num_word`
    + offset `r params$overview_choice_offset`
* book: `r books_selected`
* by hand: `r result_selection`

Analysis:

* Stopwords: `r params$stop_words`
* Normalization/Stemming: `r params$stemming`
* Data selected: `r result_selection_analysis`
* Wordcloud frequencies:
    + minimum `r mifw`
    + maximum `r mafw`
* Wordcloud maximum number of words: `r mww`
* Selected word in the wordcloud: `r selected_cloud_word`


#Pre-processing
##Filter


Boxplot results for the chosen tokenization:

* Sentences: `r params$result_choice_box_1`
* Words: `r params$result_choice_box_2`
* Word types: `r params$result_choice_box_3`
* Ratio: `r params$result_choice_box_4`
* Normalization: `r params$result_choice_box_5`

```{r warning=FALSE}
d_boxplot_1 <-  data.frame(token_sentence_col = unlist( d_token_boxplot[1]))
d_boxplot_2 <-  data.frame(token_word_ocu_col = unlist( d_token_boxplot[2]))
d_boxplot_3 <-  data.frame(token_word_type_col = unlist( d_token_boxplot[3]))
d_boxplot_4 <-  data.frame(token_ratio_col = unlist( d_token_boxplot[2])/unlist( d_token_boxplot[3]))
d_boxplot_5 <-  data.frame(token_normalization = unlist( d_token_boxplot[4]))
  
#Creating the keys for the boxplot to uniquely identify the tokenizations
# key_1_1 <-  row.names(d_boxplot_1)[-strtoi(token_sentence_radio_button())]})
# key_1_2 <-  row.names(d_boxplot_1)[strtoi(token_sentence_radio_button())]})
key_1 <-  row.names(d_boxplot_1)
key_2 <-  row.names(d_boxplot_2)
key_3 <-  row.names(d_boxplot_3)
key_4 <-  row.names(d_boxplot_4)
key_5 <-  row.names(d_boxplot_5)
  
#Doing the boxplots
  
p1_box <- plot_ly(d_boxplot_1,x = rep(0, length(d_boxplot_1$token_sentence_col)), y=~token_sentence_col, key=~key_1, type = "scatter", source = "box1", mode='markers', marker =list(color="blue"))%>%
      add_trace(d_boxplot_1, y=~token_sentence_col, type = "box")%>%layout(title = 'Box plot of the sentence tokenization', yaxis =list(title ='Number of sentences'), titlefont = 'arial', showlegend = FALSE)
    #hoverinfo = 'text', text =~paste("Maximum:", fivenum(test_d)[5], "Q3:", fivenum(test_d)[4]), marker = list(outliercolor = "red"))
    # add_trace(x = 0, y=~token_sentence_col[strtoi(token_sentence_radio_button())], key  =~ key_1_2(), marker = list(color="yellow"))%>%  

tmpFile <- tempfile(fileext = ".png")
export(p1_box, file = tmpFile)

cat(paste("Lower whisker: ", params$boxplot_1_data[1], ". First quartile: ", params$boxplot_1_data[2], ". Median: ", params$boxplot_1_data[3],
      ".", "\n", " Third quartile: ", params$boxplot_1_data[4], ". Upper whisker: ", params$boxplot_1_data[5], "."))

p2_box <- plot_ly(d_boxplot_2,x = rep(0, length(d_boxplot_2$token_word_ocu_col)), y=~token_word_ocu_col, key  =~ key_2, type = "scatter", source = "box2", mode='markers')%>%add_trace(d_boxplot_2, y=~token_word_ocu_col, type = "box",  marker = list(outliercolor = "red"))%>%layout(title = 'Box plot of the word tokenization', yaxis =list(title ='Number of words'), titlefont = 'arial', showlegend = FALSE)

tmpFile <- tempfile(fileext = ".png")
export(p2_box, file = tmpFile)

cat(paste("Lower whisker: ", params$boxplot_2_data[1], ". First quartile: ", params$boxplot_2_data[2], ". Median: ", params$boxplot_2_data[3],
      ".", "\n", " Third quartile: ", params$boxplot_2_data[4], ". Upper whisker: ", params$boxplot_2_data[5], "."))

p3_box <- plot_ly(d_boxplot_3,x = rep(0, length(d_boxplot_3$token_word_type_col)), y=~token_word_type_col, key  =~ key_3, type = "scatter", source = "box3", mode='markers')%>%add_trace(d_boxplot_3, y=~token_word_type_col, type = "box",  marker = list(outliercolor = "red"))%>%layout(title = 'Box plot of the word type tokenization', yaxis =list(title ='Number of different words'), titlefont = 'arial', showlegend = FALSE)

tmpFile <- tempfile(fileext = ".png")
export(p3_box, file = tmpFile)

cat(paste("Lower whisker: ", params$boxplot_3_data[1], ". First quartile: ", params$boxplot_3_data[2], ". Median: ", params$boxplot_3_data[3],
      ".", "\n", " Third quartile: ", params$boxplot_3_data[4], ". Upper whisker: ", params$boxplot_3_data[5], "."))

p4_box <- plot_ly(d_boxplot_4,x = rep(0, length(d_boxplot_4$token_ratio_col)), y=~token_ratio_col, key  =~ key_4, type = "scatter", source = "box4", mode='markers')%>%add_trace(d_boxplot_4, y=~token_ratio_col, type = "box",  marker = list(outliercolor = "red"))%>%layout(title = 'Box plot of the ratio', yaxis =list(title ='Ratio'), titlefont = 'arial', showlegend = FALSE)

tmpFile <- tempfile(fileext = ".png")
export(p4_box, file = tmpFile)

cat(paste("Lower whisker: ", params$boxplot_4_data[1], ". First quartile: ", params$boxplot_4_data[2], ". Median: ", params$boxplot_4_data[3],
     ".", "\n", " Third quartile: ", params$boxplot_4_data[4], ". Upper whisker: ", params$boxplot_4_data[5], "."))

p5_box <- plot_ly(d_boxplot_5,x = rep(0, length(d_boxplot_5$token_normalization)), y=~token_normalization, key  =~ key_5, type = "scatter", source = "box5", mode='markers')%>%add_trace(d_boxplot_5, y=~token_normalization, type = "box",  marker = list(outliercolor = "red"))%>%layout(title = 'Box plot of the normalization', yaxis =list(title ='Number of normalized words'), titlefont = 'arial', showlegend = FALSE)

tmpFile <- tempfile(fileext = ".png")
export(p5_box, file = tmpFile)

cat(paste("Lower whisker: ", params$boxplot_5_data[1], ". First quartile: ", params$boxplot_5_data[2], ". Median: ", params$boxplot_5_data[3],
      ".", "\n", " Third quartile: ", params$boxplot_5_data[4], ". Upper whisker: ", params$boxplot_5_data[5], "."))

```

##Details on demand
###Heaps law

This is Heaps law:

```{r}
plot(log(params$occurence_word),log(params$occurence_stop_word),main="Heaps law Log", xlab="Log of number of word occurences", ylab="Log of number of stop words")
abline(params$regression_lin)

summary(params$regression_lin)

plot(params$occurence_word, params$occurence_stop_word,main="Heaps law", xlab="Number of word occurences", ylab="Number of stop words")
lines(params$occurence_word, K*params$occurence_word^beta, col="red")
```

###Zipf's law

This is Zipf's law:

```{r}
zipfs_law_result[[4]]
zipfs_law_result[[1]] %>% ggplot(aes(rank, term_frequency)) +
      geom_abline(intercept = log(zipfs_law_result[[2]]), slope = zipfs_law_result[[3]], color = "red") +
      geom_line(size = 1.1, alpha = 0.8, show.legend= FALSE) +
      scale_x_log10() +
      scale_y_log10() + ggtitle("Zipf's law") + xlab("Rank")+ ylab("Term frequency")

# tmpFile <- tempfile(fileext = ".png")
# export(p_zipfs_res, file = tmpFile)
```

###Summary table

```{r}
kable(params$table_info_laws, caption = "Summary table")
```


#Analysis
##Overview 

You can see just below the different plots of the overview: 

```{r}
p1 <- plot_ly(d, x = ~rowname, y = ~freq, key = ~key, type = 'scatter', mode='lines+markers',  marker = list(color = 'blue', opacity=2))%>%layout(title = 'Frequency according to the word', xaxis = list(title ='Word'), yaxis =list(title ='Frequency'), titlefont = 'arial', showlegend = FALSE)
tmpFile <- tempfile(fileext = ".png")
export(p1, file = tmpFile)

p2 <- plot_ly(d, x = ~rowname, y = ~tf, key = ~key, type = 'scatter', mode='lines+markers',  marker = list(color = 'blue', opacity=2))%>%layout(title = 'Term Frequency according to the word', xaxis = list(title ='Word'), yaxis =list(title ='Term Frequency'), titlefont = 'arial', showlegend = FALSE)
tmpFile <- tempfile(fileext = ".png")
export(p2, file = tmpFile)
```

##Filter

###Plots

You can see here the different plots of the overview after selection of the interesting points:

```{r}
if(l!=0){
  key_part = row.names(ds)
  
  p3 <- plot_ly(ds, x = ~rowname, y = ~freq, key = ~key_part, type = 'scatter', mode='lines+markers',  marker = list(color = 'blue', opacity=2))%>%layout(title = 'Frequencies according to the selected words', xaxis = list(title ='Word'), yaxis =list(title ='Frequency'), titlefont = 'arial', showlegend = FALSE)
  tmpFile <- tempfile(fileext = ".png")
  export(p3, file = tmpFile)
}
```

```{R}
if(l!=0){
  p4 <- plot_ly(ds, x = ~rowname, y = ~tf, key = ~key_part, type = 'scatter', mode='lines+markers',  marker = list(color = 'blue', opacity=2))%>%layout(title = 'Term Frequencies according to the selected words', xaxis = list(title ='Word'), yaxis =list(title ='Term Frequency'), titlefont = 'arial', showlegend = FALSE)
  tmpFile2 <- tempfile(fileext = ".png")
  export(p4, file = tmpFile2)
}
```

###Table

Here is the table with the selected points from the overview:

```{r}
if(l){
kable(params$data_table_selected_plot, caption ="Table of the data selected in the plot")
}
```

###Wordcloud

You can see just below the wordcloud with the interesting points :

```{r}
bp.cols<- c("light blue","cornflowerblue", "coral2", brewer.pal(8,"Dark2"))
dsw <- data.frame(ds$word, ds$freq)
dswf <- head(subset(dsw, dsw$ds.freq <= mafw & dsw$ds.freq >= mifw), mww)
if(l){
  library(wordcloud)
  #This part is to add a title to the wordcloud. In order to do that, you have to change the layout before adding the title. It is explained here :     https://stackoverflow.com/questions/15224913/r-add-title-to-wordcloud-graphics-png
  layout(matrix(c(1, 2), nrow=2), heights=c(1, 4))
  par(mar=rep(0, 4))
  plot.new()
  text(x=0.5, y=0.5, cex = 0.8, "Wordcloud 1 : Wordcloud of the selected points")
  #This is where we do the wordcloud, adding some colors and some other features.
  wordcloud(dswf$ds.word, dswf$ds.freq, random.order=FALSE,rot.per=0.40,use.r.layout=FALSE, random.color=TRUE,colors=bp.cols, main=text)
}
#w <- wordcloud2(data = dswf, shape = 'star', size = 0.8, shuffle =FALSE)
#tmpFile <- tempfile(fileext = ".png")
#export(w, file = tmpFile)
```

##Details on demand
###Table

```{r}
kable(params$sentences_selected_cloud, caption = paste("Sentences associated with", `r selected_cloud_word`))   
```

###Wordcloud

Wordcloud of the words in the same sentence as `r params$selected_word_cloud`

```{r}
bp.cols<- c("light blue","cornflowerblue", "coral2", brewer.pal(8,"Dark2"))
if(l){
  library(wordcloud)
  #This is where we do the wordcloud, adding some colors and some other features.
  wordcloud(d_last_wd$word, d_last_wd$freq, random.order=FALSE,rot.per=0.40,use.r.layout=FALSE, random.color=TRUE,colors=bp.cols)
}
#w <- wordcloud2(data = dswf, shape = 'star', size = 0.8, shuffle =FALSE)
#tmpFile <- tempfile(fileext = ".png")
#export(w, file = tmpFile)
```